---
title: "Coursera Building Data Products - Week 3 Assignment"
author: "Amyn"
date: '2017-02-12'
output: slidy_presentation
---

## Assignment Description
- Create a web page presentation using R Markdown that features a plot created with Plotly. 
- Host your webpage on either GitHub Pages, RPubs, or NeoCities. 
- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 
- We would love to see you show off your creativity!

## Review Criteria
- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Get Started
- Set the working directory
- Load the Plotly Library
- Load the Diamond Data Set

```{r, echo = FALSE}
setwd("~/Documents/R Working Directory/Course_9_Data_Products/C9_Wk3")
library(plotly)
data("diamonds")

```

## Diamond Price Plot
- Plot the price of diamonds as a function of the number of carrots and the diamond color

```{r, echo = FALSE}
plot_ly(diamonds, x = ~carat, y = ~price, color = ~color, text = ~paste("Clarity: ", clarity))
```
